Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-24 paper/paper.tex
Remove old first paragraph.

\section*{Introduction}
Determining the similarity of two users or items is valuable for a
number of data-mining applications including recommender systems, product
assortment and differentiation, and branding. Collaborative filtering is
often used to exploit user-item rating data to make such estimates. This is 
typically done by computing the Pearson correlation or cosine similarity of 
vector representations of the users or items \cite{Breese98}. Given sufficient 
user-item rating data, this approach can be very effective. However, when the
rating data is sparse for one or both users/items, these metrics can
yield dramatic discrepancies compared to values computed with sufficient
data at a later point in time. In this report, we describe two novel techniques 
for estimating the true similarity of two users or items given limited common 
rating data.

...
Accurate estimations of the similarity of two users or items is valuable for a
number of data-mining applications including recommender systems, product
assortment and differentiation, as well as branding. Collaborative filtering is
often used to exploit user-item rating data to make such estimates typically by
computing the Pearson correlation or cosine similarity of vector representations
of the users or items \cite{Su2009}. Given sufficient user-item rating data,
this approach can be very effective. On the otherhand, when very little rating
data for one or both users/items is available, unmodified, these metrics can
yield dramatic discrepancies compared to values computed later once sufficient
data has been acquired. In this report, we describe two novel techniques for
estimating the true similarity of two users or items given limited common rating
data.

>>>>

\section*{Introduction}
Determining the similarity of two users or items is valuable for a
number of data-mining applications including recommender systems, product
assortment and differentiation, as well as branding. Collaborative filtering is
often used to exploit user-item rating data to make such estimates. This is 
typically done by computing the Pearson correlation or cosine similarity of 
vector representations of the users or items \cite{Su2009}. Given sufficient 
user-item rating data, this approach can be very effective. However, when the
rating data is sparse for one or both users/items, these metrics can
yield dramatic discrepancies compared to values computed with sufficient
data at a later point in time. In this report, we describe two novel techniques 
for estimating the true similarity of two users or items given limited common 
rating data.
